---
title: "Test tutorial for the learnrextra package"
runtime: shiny_prerendered
author: Markus Konrad
email: markus.konrad@htw-berlin.de
date: "`r format(Sys.time(), '%d.%m.%Y')`"
output:
    learnrextra::tutorial:
        language: en
        apiserver: http://localhost:8000/
---

```{r setup, include=FALSE}
require(RAppArmor)     # necessary on server
library(learnr)        # for quizzes, code exercises, etc.
library(learnrextra)
library(gradethis)     # for evaluating code exercises
library(shiny)         # for interactive elements

knitr::opts_chunk$set(echo = FALSE)
```

## Page 1 – quizzes and code exercises

Example quiz with single correct choice.

```{r quiz1}
question("Example question.",
  answer("Example answer 1."),
  answer("Example answer 2 (correct).", correct = TRUE),
  answer("Example answer 3."),
  allow_retry = TRUE
)
```

Example quiz with multiple correct choices.

```{r quiz2}
question("Example question.",
  answer("Example answer 1 (correct).", correct = TRUE),
  answer("Example answer 2."),
  answer("Example answer 3 (correct).", correct = TRUE),
  allow_retry = TRUE
)
```

```{r quiz3}
question_mathexpression("Enter 3.14 or any calculation that leads to 3.14",
  expected_result = 3.14,
  correct_repeat_result = TRUE,
  allow_retry = TRUE
)
```

```{r quiz4}
question_mathexpression_probability("Enter the probability of heads for a fair coin.",
  expected_result = 0.5,
  allow_retry = TRUE
)
```

```{r quiz5}
question_mathexpression_percentage("Enter the probability of heads for a fair coin in percent.",
  expected_result = 50,
  allow_retry = TRUE
)
```

```{r survey}
survey_items <- list(
    list(
        text = "Single choice question.",
        answers = c("One.", "Two.")
    ),
    list(
        text = "Multiple choice question.",
        answers = c(
            "foo" = "Foo.",
            "bar" = "Bar.",
            "foobar" = "Foobar."
        ),
        type = "learnr_checkbox"
    ),
    list(
        text = "Free text question",
        type = "learnr_text"
    ),
    list(
        text = "Numeric answer between 1 and 5",
        type = "learnr_numeric",
        question_args = list(min = 1, max = 5, step = 1)
    )
)

survey(survey_items)
```


```{r survey_likert1}
survey_likert(c("Likert question 1", "Likert question 2"),
              c("agree", "undecided", "don't agree"),
              caption = "Likert scale survey 1")
```


```{r survey_likert2}
survey_likert(c("likert3" = "Likert question 3",
                "likert4" = "Likert question 4"),
              list(
                  c("-1" = "bad", "0" = "neutral", "1" = "positive"),
                  c("foo" = "FOO", "bar" = "BAR")
              ),
              caption = "Likert scale survey 2")
```



**Example code exercise.** Fill in the gaps to generate 100 samples from a normal distribution with mean $\mu=-1$ and
standard deviation $\sigma=3$. Report mean and standard deviation of the drawn samples.

```{r code1, exercise=TRUE, exercise.timelimit=5, exercise.blanks = "___+"}
x <- ___(100, mean = -1, sd = 3)  # draw samples
c(___, ___)  # report mean and SD
```

```{r code1-solution}
x <- rnorm(100, mean = -1, sd = 3)  # draw samples
c(mean(x), sd(x))  # report mean and SD
```

```{r code1-check}
grade_this_code()
```


## Page 2 – Shiny inputs


```{r}
checkboxInput("checkbox_input_test", "checkbox input test")
dateInput("date_input_test", "date input test")
dateRangeInput("date_range_input_test", "date range input test")
numericInput("numeric_input_test", "num. input test", 0)
radioButtons("radio_buttons_test", "radio buttons test", c("foo", "bar"))
selectInput("select_input_test", "select input test", c("foo", "bar"))
sliderInput("slider_input_test", "slider input test", 1, 10, 5, step = 1)
textInput("text_input_test", "text input test")
textAreaInput("text_input_test", "text area input test")
```

::: tracking_consent_text

This is an example tracking consent information text.

The following data is being recorded while interacting with this website:

<ul>
    <li>information on your browser (browser software, window dimensions)</li>
    <li>start and end time when using this website</li>
    <li class="trackingdata-chapters">changes between pages</li>
    <li>information on quiz trials (given answers, results)</li>
    <li>information on code exercises (submitted code, result, success)</li>
    <li class="trackingdata-inputs">changes to input elements (e.g. sliders for interactive graphics)</li>
    <li class="trackingdata-mouse">mouse movements</li>
    <li class="trackingdata-mouse">page scrolls</li>
    <li class="trackingdata-mouse">clicks</li>
</ul>


:::

::: data_protection_text

This is an example data protection text.

...

:::
